DPIV Analysis and Real Time Implementation

### 2023-01-02 Paper/main.tex
Comments

\DS{Provide a little bit of scientific context where DPIV has been used. I would try to make a small search if a part from this work~\cite{2017-CaiSanBucOrtCabInt}, offline/online versions have been presented.  }
In this paper, a DPIV online platform implementation for data acquisition and processing is proposed. Starting from a pre-existing DPIV platform that works offline\DS{add reference and refer to the previous work}, a new version of the same algorithm
that works online has been implemented. The feature that most diversifies the two algorithms is based on the fact that the offline algorithm works on a video acquired in a moment before the analysis that is carried out and through a different software from the one on which the analysis routine runs.
\DS{In general I would try to go directly to the point without adding long sentences as "is based on the fact that"}
\DS{My proposal would be: The key distinction between the two approaches is that the offline algorithm operates on a video captured at an earlier time and uses a slight different software platform than the one employed for the online analysis. }
~\fig\ref{Algorithms} shows a schematic of the two implementations and highlights the main differences.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=1\columnwidth]{images/frames}
	\centering{\caption{\label{frame} Offline and Online frame in comparison with the same camera parameters. Region of Interest (ROI) coordinates selection in the Online frame. }}
\end{figure}

Both implementations share the initial steps of establishing the camera's settings by making adjustments to the pixel size parameters listed in the camera datasheet, the desired magnification, the exposure time and the image gain. \DS{I tried to wirte down these concepts in a less schematical way. You've done a good job by changing them from bullet lists to this format. I leave the other parts of the text for you, so that you can try to rewrite them as I wrote this one. Additional details about the image gain could be provided.}
The major difference of the online version is represented by the acquisition that takes place in an online mode through the communication between the CCD camera and the PC. \DS{I would add these implementation details about the software in the experimental setup. I'd focus on the methodology in this section. } MATLAB downloading the \textbf{Windows SDK and Doc. for Scientific Cameras}. This allows to capture process frames directly from the MATLAB routine and they are ready to be used for the analysis. The Offline version, on the other hand, provides for a further step of uploading on MATLAB the video previously acquired through a dedicated software and unpack it into the corresponding frames. 
Online frames acquisition through MATLAB allows to obtain a higher resolution process frame for the same camera parameters as it is shown in ~\fig\ref{frame}\DS{to be verified}.
Having the data available, the algorithm proceeds in a similar way in the two platforms\DS{I'd rather call them implementations rather then platforms}.
\newcommand{\abscissa}{x}
\newcommand{\ordinate}{y}
\newcommand{\mean}[1]{<V_{#1}(t)>}
\newcommand{\spatialmean}[3]{V_{#1}({#2},{#3},t)}

An on-screen ROI selection procedure allows setting the left-top corner of the image as the starting pixel and the right-down corner of the image as the end pixel. The resulting coordinates for the selection of the ROI are represented in ~\fig\ref{frame}: the abscissa ($\abscissa$) and ordinate ($\ordinate$) of the left-top point and the width ($W_{ROI}$) and height ($H_{ROI}$) of the region itself, obtained from the selection of the right-down point. \DS{Try to define the symbols so that when you want to reuse them, it will be faster. Try to follow the commands I defined and try to use this approach for the whole text. It will be very useful in the next future. I'm leaving them in the text for the moment.}
A DPIV analysis followed by a micro-particles counting procedure are at this point carried out for the predefined interrogation Regions of Interest (ROIs)\DS{You've already defined it.}. A DPIV-based algorithm provides instantaneous velocity measurements and visualization. The DPIV approach consists of a first collection of the time-varying velocity vector maps through the evaluation of the cross-correlation between ROIs of consecutive pairs of images \DS{I'd try to provide some context saying that you're going to summarize in few lines the approach}. 

@@

 \begin{enumerate}
 	\item ROI selection;
 	\item Conversion to greyscale;
 	\item Duplication of the image;
 	\item Application of a gaussian filter (radius equal to 5);
 	\item Difference between the original image and the duplicated one;
 	\item Binarization of the image;
 \end{enumerate}
At this point a function takes as input the binary image. It traces the exterior boundaries of particles and gives the number of them found.
Important parameters to be set are the minimum and maximum dimensions of the searched object in pixels, in order to count among the found micro-particles only those that have an appropriate size. For the yeast cells and the silica beads the minimum area was set to 1 pixel and the maximum was set to 2 pixels \DS{measurement units and, so far, focus on the methodology rather than the experimental details. They will be given in the next section.}. There is another parameter to be set based on the shape of the object that is \DS{Try to sump up this long preparatory sentence} a threshold value chosen to define the circularity. Due to the circular geometry of the micro-particles, the threshold was set equal to 1 that indicates a perfect circle \DS{Again, try to describe the approach in its general form. Futher details about the numbers, shapes and so on, will be provided after}.
Having defined all the parameters, the exterior boundaries of micro-particles are traced and the number of them is found for each frame.

@@

A magnification of 10X (PLN, Olympus, Tokyo, Japan) has been used to scale up the channel images to be able to see more detail and increasing resolution.
Acquisitions and analyzes were performed using a SAMSUNG Galaxy Book PC, with an Intel Core i7 processor, INTEL Iris Xe Graphics, 16 GB RAM and 512 GB SSD.
\\The fluids employed for the experiments were obtained by diluting micro-particles in different solutions. The micro-particles were of two types: cells of eukaryotic origins with a diameter of 5 $[\rm\mu m]$ and artificial silica beads with a diameter of 6 $[\rm\mu m]$. Two types of particles have been used to investigate and compare the different behaviors of cells and synthetic particles. Their physical properties, such as mass, radius, volume and density, are summerized in ~\tab\ref{properties}. Four different types of yeast cell living conditions have been examined. In particular viable cells, 2 days overgrowth, 5 days overgrowth and exposed to cell death stimuli with hydrogen peroxide ($H_2O_2$) \DS{Viable and death cells. I wouldn't mention the others}. 
Yeast cells were diluted in a saline solution, the phospate buffered saline (PBS, density of 1072 $Kg/m^3$). By contrast, Silica beads micro-particles were diluted in two different solutions. A first one (density of 1200 $Kg/m^3$) obtained by combining 20\% of water with 80\% of glycerol to avoid the deposition of the particles at the bottom of the channel thanks to the increment of the fluid density. The second solution is represented by PBS.
The microfluidic chip was fed with fluid on which an oscillating flow was imposed.
At the beginning a PBS flow and then a glycerol-water flow, without micro-particles suspendend on it, was recorded to quantify the effect of the fluid backgroung in the images. It was injected through syringe pumps with an external oscillating pressure at a frequency of $f_i= 0.1 Hz$ and an amplitude of $A=0.1 ml/min$. \DS{please, define the symbols} 
\\The other 40 experiments that have been carried out are summarized in ~\tab\ref{offlineexp} and ~\tab\ref{onlineexp}, distinguished according to the software platform used to analyze them (Offline or Online \DS{no need to use capital letters,}). Experiments with viable yeast cells and beads in glycerol-water solution were performed twice, to compare the results obtained with the two different implementations and test their consistency.
For all categories of cells and particles, the sample of fluid was fed into the micro-channel using an oscillating flow at a fixed frequency of $f_i= 0.1 Hz$ and five different amplitude values $A \in{0.05, 0.07, 0.1, 0.15, 0.2 ml/min}$. \DS{let's use the same style for the unit measurements}

@@

\begin{table}[h!]
	\begin{tabular}{@{}lcccc@{}}
		\toprule
		\multicolumn{5}{c}{\textbf{Region of Interest (ROI)}}                                                                                         \\ \midrule
		& \textbf{$x$} & \textbf{$y$} & \textbf{$H_{ROI}$} & \textbf{$W_{ROI}$} \\
		\textit{Yeast cells}  & 6          & 131        & 473                                          & 360                                          \\
		\textit{Silica beads} & 7          & 67         & 467                                          & 411                                          \\ \bottomrule
	\end{tabular}
	\centering{\caption{\label{roi}Region of Interest (ROI) coordinates set for the image area acquired and analyzed in the performed experiments. }}
\end{table}

@@

\section{Results and discussion}
\DS{Before the entire discussion, I often use to summarize what the reader is going to read in the next few lines. For example, in \sect\ref{sec:suspended-particles} we will discuss this ..., in \sect\ref{sec:comparison} we will compare that... Referring to the methodology as you did if you like.}
Since the micro-particles are induced to move in the horizontal direction, this will be the component considered in the subsequent analysis. 
%Looking at the movement of the micro-particles along the micro-channel and considering also the image orientation, the dominant velocity component is the horizonatal one. In fact, the trend of the horizontal velocity component $<V_x(t)>$ shows the periodicity of the oscillating input flow imposed. This component is the one taken in consideration for the following analysis. 
\\The micro-particles hydrodynamic response in time domain was evaluated by computing the range of the velocity signal $<V_x(t)>$, according to \DS{\eqn} \ref{eqn:range}. 
\begin{equation}
	\label{eqn:range}
	Range<V_x(t)>=max(<V_x(t)>)-min(<V_x(t)>)
\end{equation}
The micro-particles hydrodynamic response in frequency domain was evaluated by computing the spectrum of the velocity signal $<V_x(t)>$, in order to obtain information on the frequency components involved in the dynamic process.
\DS{Maybe this part can go in the methodology section, so that you will need to refer to it rather than write it. Besides, you could also add more details about its meaning. In fact, it is more about the methodology rather than related to the results.}

@@

The micro-particles hydrodynamic response in time domain was evaluated by computing the range of the velocity signal $<V_x(t)>$, as shown in \DS{\eqn(}\ref{eqn:range}). ~\fig\ref{BeadsFinal} shows the value of the velocity range ($Range<V_x(t)>$) and the peak at the fundamental frequency ($Amplitude peak$ \DS{we should define a symbol for this quantity. A letter would be enough.}) for each experimental condition. The two curves are related to silica beads in the two different solutions considered and each point of the curves is correlated to the amplitude of the external oscillating input flow strength $A$ with a constant frequency $f_i= 0.1 Hz$. 
\\The curve related to the beads in PBS does not show any correlation between the imposed input and the hydrodynamic response of the micro-particles. The curve relating to the beads in the glycerol-water solution shows how the parameters examined in the time domain and in the frequency domain increase as the input amplitude increases, showing a correlation between the input and the hydrodynamic response of the micro-particles.

@@

In ~\fig\ref{Yeast}, for viable and exposed to cell death stimuli yeast cells, in the experimental condition with {$A=0.1 ml/min, f_i= 0.1 Hz$} and in a time interval of about 60 $s$ \DS{no need to re-write the same information about the experimental analysis. We've already said how much time we record the data. We should find labels to identify each experiment so that the reading would be smoother.}, the velocity signals in the dominant component  $<V_x(t)>$ \DS{not a fun of this $< V >$ way of describing the mean. We could use $\bar{V}$} are plotted. The different oscillating trends of the velocity signals highlights the effects induced by the oscillating input flow in different cell living condition. In particular, considering the same experimental condition, the amplitude of the velocity trend for viable yeast cells (see ~\fig\ref{Yeast}(a)) is lower than the one found for yeast cells exposed to cell death stimuli. 
In the condition of viable yeast cells there is a greater resistance from the cells to the force imposed on the input, resulting in a lower maximum speed value reached compared to that of yeast cells exposed to cell death stimuli.

@@

In ~\fig\ref{VelPar} the superposition of the trend of  $<V_x(t)>$ and the trend of $<N_p(t)>$ is plotted, in the experimental condition with viable yeast cells and {$A=0.1 ml/min, f_i= 0.1 Hz$}. In the instants in which the speed signal is 0 \DS{measurement unit?}, the signal of the trend of the particles assumes the maximum value; this is due to the fact that when the speed is zero, particles stop and accumulate.
\\In the instants in which the velocity signal is at the maximum or minimum value, the particle trend signal assumes the minimum value, because particles are in motion, in one direction or in the other, and the fewest number of them are counted by the algorithm. This is a consequence of the hydrodynamic stimulus imposed by the mechanical actuation through the syringe pumps flow rate, i.e. particles tend to be highly concentrated when the stimulus reaches the zero value, otherwise they are more dispersed during the rising phase of the stimulus, indipendently of its direction. \DS{After the discussion, it should be clear why we're using the counting algorithm. We need it for the normalization. Therefore, I would consider to add a small sentence about that. This will make the reader conscious of the reason why we need a counting algorithm for the approach. Let's try to find the best spot for this small explanation so that we do not have repetition in the text.}

\begin{figure}[t]
	\centering
	\includegraphics[width=1\columnwidth]{images/Comparison}
	\centering{\caption{\label{Comparison}The parameter ($Range<V_x(t)>$) varying the oscillating input flow strength at the inlet $A$ at a frequency $f_i= 0.1 Hz$: comparison between viable yeast cells, yeast cells exposed to cell death stimuli and silica beads in the glycerol-water (GW) solution.\DS{How do you do these curves? Why do they show this curvilinear behavior and not a rectilinear one?}}}
\end{figure}

~\fig\ref{Comparison} shows the value of the velocity range ($Range<V_x(t)>$ \DS{no need to repeat this symbol. Once defined, you can just refer to the symbol}) for each experimental condition. The three curves are related to viable yeast cells, yeast cells exposed to cell death stimuli and silica beads in the glycerol-water solution. Each point of the curves is correlated to the amplitude of the external oscillating input flow strength $A$ with a constant frequency $f_i= 0.1 Hz$. 
Because of the fact that micro-particles of different natures are being compared, a normalization of the $Range<V_x(t)>$ to the average number of particles was carried out. This procedure was applied due to the fact that the micro-particles density is different in each experimental condition and thanks to this normalization it is possible to compare the results obtained. 
\\The micro-particles hydrodynamic response comparison in time domain was evaluated by computing the range of the velocity signal $<V_x(t)>$, as shown in \DS{\eqn(}\ref{eqn:range}) and normalizing it with respect to the average number of micro-particles $<N_p(t)>$, computed in the investigated area following the procedure described in \sect\ref{sec:method}.
From ~\fig\ref{Comparison} it is possible to notice that, for all the experimental conditions, the curve relating to yeast cells exposed to cell death stimuli is always in the middle, between the one relating to viable yeast cells and the one relating to silica beads in the glycerol-water solution.
Yeast cells vary their behavior according to their different living conditions taking on characteristics more typical of synthetic particles, i.e. silica beads, when they are exposed to death stimuli. In fact, the results show that their behavior is comparable with particles of lower density and with the fluid on which they are suspended as they exhibit no resistance to the input flows while attaining higher velocities than the yeast live cells.

\subsection{Online vs Offline}\label{sec:OnlineOffline}
\DS{Before going into the details with this part and its revision, please, consider to make all the necessary steps to identify that the camera settings are not modified by Matlab. }
To test the consistency of the two DPIV-based implementations, a subset of the experiments was tested and analyzed also through the DPIV-based online implementation, detailed in ~\tab\ref{onlineexp}. Two categories of micro-particles were considered, more precisely viable yeast cells and silica beads in the glycerol-water solution. The sample of fluid was fed into the micro-channel using an oscillating flow at a fixed frequency of $f_i= 0.1 Hz$ and five different amplitude values $A \in \{ 0.05, 0.07, 0.1, 0.15, 0.2 ml/min \}$. Process frames were acquired for a time interval of 15 $s$ for each experimental condition. 
The results obtained through the online platform\DS{implementation} were compared with those obtained through the offline platform for the same micro-particle category and experimental conditions. \DS{measurement units}

>>>>

\DS{OK ---- Provide a little bit of scientific context where DPIV has been used. I would try to make a small search if a part from this work~\cite{2017-CaiSanBucOrtCabInt}, offline/online versions have been presented.  }
In this paper, a DPIV online platform implementation for data acquisition and processing is proposed. Starting from a pre-existing DPIV platform that works offline\DS{OK ---- add reference and refer to the previous work}, a new version of the same algorithm
that works online has been implemented. The feature that most diversifies the two algorithms is based on the fact that the offline algorithm works on a video acquired in a moment before the analysis that is carried out and through a different software from the one on which the analysis routine runs.
\DS{OK ---- In general I would try to go directly to the point without adding long sentences as "is based on the fact that"}
\DS{My proposal would be: The key distinction between the two approaches is that the offline algorithm operates on a video captured at an earlier time and uses a slight different software platform than the one employed for the online analysis. }
~\fig\ref{Algorithms} shows a schematic of the two implementations and highlights the main differences.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=1\columnwidth]{images/frames}
	\centering{\caption{\label{frame} Offline and Online frame in comparison with the same camera parameters. ROI coordinates selection in the Online frame. }}
\end{figure}

Both implementations share the initial steps of establishing the camera's settings by making adjustments to the pixel size parameters listed in the camera datasheet, the desired magnification, the exposure time and the image gain. \DS{I tried to wirte down these concepts in a less schematical way. You've done a good job by changing them from bullet lists to this format. I leave the other parts of the text for you, so that you can try to rewrite them as I wrote this one. Additional details about the image gain could be provided.}
The major difference of the online version is represented by the acquisition that takes place in an online mode through the communication between the CCD camera and the PC. \DS{I would add these implementation details about the software in the experimental setup. I'd focus on the methodology in this section. } MATLAB downloading the \textbf{Windows SDK and Doc. for Scientific Cameras}. This allows to capture process frames directly from the MATLAB routine and they are ready to be used for the analysis. The Offline version, on the other hand, provides for a further step of uploading on MATLAB the video previously acquired through a dedicated software and unpack it into the corresponding frames. 
Online frames acquisition through MATLAB allows to obtain a higher resolution process frame for the same camera parameters as it is shown in ~\fig\ref{frame}\DS{OK ---- to be verified}.
Having the data available, the algorithm proceeds in a similar way in the two implementations. 
\newcommand{\abscissa}{x}
\newcommand{\ordinate}{y}
\newcommand{\mean}[1]{<V_{#1}(t)>}
\newcommand{\spatialmean}[3]{V_{#1}({#2},{#3},t)}

An on-screen Region of Interest (ROI) selection procedure allows setting the left-top corner of the image as the starting pixel and the right-down corner of the image as the end pixel. The resulting coordinates for the selection of the ROI are represented in ~\fig\ref{frame}: the abscissa ($\abscissa$) and ordinate ($\ordinate$) of the left-top point and the width ($W_{ROI}$) and height ($H_{ROI}$) of the region itself, obtained from the selection of the right-down point. \DS{OK ---- Try to define the symbols so that when you want to reuse them, it will be faster. Try to follow the commands I defined and try to use this approach for the whole text. It will be very useful in the next future. I'm leaving them in the text for the moment.}
A DPIV analysis followed by a micro-particles counting procedure are at this point carried out for the predefined interrogation ROIs. A DPIV-based algorithm provides instantaneous velocity measurements and visualization. The DPIV approach consists of a first collection of the time-varying velocity vector maps through the evaluation of the cross-correlation between ROIs of consecutive pairs of images \DS{OK ---- I'd try to provide some context saying that you're going to summarize in few lines the approach}. 

@@

 \begin{enumerate}
 	\item ROI selection;
 	\item Conversion to greyscale;
 	\item Duplication of the image;
 	\item Application of a gaussian filter (radius equal to 5);
 	\item Difference between the original image and the duplicated one;
 	\item Binarization of the image;
 \end{enumerate}
At this point a function takes as input the binary image. It traces the exterior boundaries of particles and gives the number of them found.
Important parameters to be set are the minimum and maximum dimensions of the searched object in pixels, in order to count among the found micro-particles only those that have an appropriate size. For the yeast cells and the silica beads the minimum area was set to 1 pixel and the maximum was set to 2 pixels \DS{measurement units and, so far, focus on the methodology rather than the experimental details. They will be given in the next section.}. There is another parameter to be set based on the shape of the object that is \DS{OK ---- Try to sump up this long preparatory sentence} a threshold value chosen to define the circularity. Due to the circular geometry of the micro-particles, the threshold was set equal to 1 that indicates a perfect circle \DS{Again, try to describe the approach in its general form. Futher details about the numbers, shapes and so on, will be provided after}.
Having defined all the parameters, the exterior boundaries of micro-particles are traced and the number of them is found for each frame.

@@

A magnification of 10X (PLN, Olympus, Tokyo, Japan) has been used to scale up the channel images to be able to see more detail and increasing resolution.
Acquisitions and analyzes were performed using a SAMSUNG Galaxy Book PC, with an Intel Core i7 processor, INTEL Iris Xe Graphics, 16 GB RAM and 512 GB SSD.
\\The fluids employed for the experiments were obtained by diluting micro-particles in different solutions. The micro-particles were of two types: cells of eukaryotic origins with a diameter of 5 $[\rm\mu m]$ and artificial silica beads with a diameter of 6 $[\rm\mu m]$. Two types of particles have been used to investigate and compare the different behaviors of cells and synthetic particles. Their physical properties, such as mass, radius, volume and density, are summerized in ~\tab\ref{properties}. Four different types of yeast cell living conditions have been examined. In particular viable cells, 2 days overgrowth, 5 days overgrowth and exposed to cell death stimuli with hydrogen peroxide ($H_2O_2$) \DS{Viable and death cells. I wouldn't mention the others}. 
Yeast cells were diluted in a saline solution, the phospate buffered saline (PBS, density of 1072 $Kg/m^3$). By contrast, Silica beads micro-particles were diluted in two different solutions. A first one (density of 1200 $Kg/m^3$) obtained by combining 20\% of water with 80\% of glycerol to avoid the deposition of the particles at the bottom of the channel thanks to the increment of the fluid density. The second solution is represented by PBS.
The microfluidic chip was fed with fluid on which an oscillating flow was imposed.
At the beginning a PBS flow and then a glycerol-water flow, without micro-particles suspendend on it, was recorded to quantify the effect of the fluid backgroung in the images. It was injected through syringe pumps with an external oscillating pressure at a frequency of $f_i= 0.1 Hz$ and an amplitude of $A=0.1 ml/min$. \DS{OK ---- please, define the symbols} 
\\The other 40 experiments that have been carried out are summarized in ~\tab\ref{offlineexp} and ~\tab\ref{onlineexp}, distinguished according to the software platform used to analyze them (offline or online). Experiments with viable yeast cells and beads in glycerol-water solution were performed twice, to compare the results obtained with the two different implementations and test their consistency.
For all categories of cells and particles, the sample of fluid was fed into the micro-channel using an oscillating flow at a fixed frequency of $f_i= 0.1 Hz$ and five different amplitude values $A \in{0.05, 0.07, 0.1, 0.15, 0.2 ml/min}$. \DS{let's use the same style for the unit measurements}

@@

\begin{table}[h!]
	\begin{tabular}{@{}lcccc@{}}
		\toprule
		\multicolumn{5}{c}{\textbf{Region of Interest (ROI)}}                                                                                         \\ \midrule
		& \textbf{$x$} & \textbf{$y$} & \textbf{$H_{ROI}$} & \textbf{$W_{ROI}$} \\
		\textit{Yeast cells}  & 6          & 131        & 473                                          & 360                                          \\
		\textit{Silica beads} & 7          & 67         & 467                                          & 411                                          \\ \bottomrule
	\end{tabular}
	\centering{\caption{\label{roi}ROI coordinates set for the image area acquired and analyzed in the performed experiments. }}
\end{table}

@@

\section{Results and discussion}
\DS{OK ---- Before the entire discussion, I often use to summarize what the reader is going to read in the next few lines. For example, in \sect\ref{sec:suspended-particles} we will discuss this ..., in \sect\ref{sec:comparison} we will compare that... Referring to the methodology as you did if you like.}
Since the micro-particles are induced to move in the horizontal direction, this will be the component considered in the subsequent analysis. 
%Looking at the movement of the micro-particles along the micro-channel and considering also the image orientation, the dominant velocity component is the horizonatal one. In fact, the trend of the horizontal velocity component $<V_x(t)>$ shows the periodicity of the oscillating input flow imposed. This component is the one taken in consideration for the following analysis. 
\\The micro-particles hydrodynamic response in time domain was evaluated by computing the range of the velocity signal $<V_x(t)>$, according to \eqn \ref{eqn:range}. 
\begin{equation}
	\label{eqn:range}
	Range<V_x(t)>=max(<V_x(t)>)-min(<V_x(t)>)
\end{equation}
The micro-particles hydrodynamic response in frequency domain was evaluated by computing the spectrum of the velocity signal $<V_x(t)>$, in order to obtain information on the frequency components involved in the dynamic process.
\DS{Maybe this part can go in the methodology section, so that you will need to refer to it rather than write it. Besides, you could also add more details about its meaning. In fact, it is more about the methodology rather than related to the results.}

@@

The micro-particles hydrodynamic response in time domain was evaluated by computing the range of the velocity signal $<V_x(t)>$, as shown in \eqn \ref{eqn:range}. ~\fig\ref{BeadsFinal} shows the value of the velocity range ($Range<V_x(t)>$) and the peak at the fundamental frequency ($Amplitude peak$ \DS{we should define a symbol for this quantity. A letter would be enough.}) for each experimental condition. The two curves are related to silica beads in the two different solutions considered and each point of the curves is correlated to the amplitude of the external oscillating input flow strength $A$ with a constant frequency $f_i= 0.1 Hz$. 
\\The curve related to the beads in PBS does not show any correlation between the imposed input and the hydrodynamic response of the micro-particles. The curve relating to the beads in the glycerol-water solution shows how the parameters examined in the time domain and in the frequency domain increase as the input amplitude increases, showing a correlation between the input and the hydrodynamic response of the micro-particles.

@@

In ~\fig\ref{Yeast}, for viable and exposed to cell death stimuli yeast cells, in the experimental condition with {$A=0.1 ml/min, f_i= 0.1 Hz$} and in a time interval of about 60 $s$ \DS{OK ---- no need to re-write the same information about the experimental analysis. We've already said how much time we record the data. We should find labels to identify each experiment so that the reading would be smoother.}, the velocity signals in the dominant component  $<V_x(t)>$ \DS{not a fun of this $< V >$ way of describing the mean. We could use $\bar{V}$} are plotted. The different oscillating trends of the velocity signals highlights the effects induced by the oscillating input flow in different cell living condition. In particular, considering the same experimental condition, the amplitude of the velocity trend for viable yeast cells (see ~\fig\ref{Yeast}(a)) is lower than the one found for yeast cells exposed to cell death stimuli. 
In the condition of viable yeast cells there is a greater resistance from the cells to the force imposed on the input, resulting in a lower maximum speed value reached compared to that of yeast cells exposed to cell death stimuli.

@@

In ~\fig\ref{VelPar} the superposition of the trend of  $<V_x(t)>$ and the trend of $<N_p(t)>$ is plotted, in the experimental condition with viable yeast cells and {$A=0.1 ml/min, f_i= 0.1 Hz$}. In the instants in which the speed signal is 0 \DS{OK ---- measurement unit?}, the signal of the trend of the particles assumes the maximum value; this is due to the fact that when the speed is zero, particles stop and accumulate.
\\In the instants in which the velocity signal is at the maximum or minimum value, the particle trend signal assumes the minimum value, because particles are in motion, in one direction or in the other, and the fewest number of them are counted by the algorithm. This is a consequence of the hydrodynamic stimulus imposed by the mechanical actuation through the syringe pumps flow rate, i.e. particles tend to be highly concentrated when the stimulus reaches the zero value, otherwise they are more dispersed during the rising phase of the stimulus, indipendently of its direction. \DS{OK ---- After the discussion, it should be clear why we're using the counting algorithm. We need it for the normalization. Therefore, I would consider to add a small sentence about that. This will make the reader conscious of the reason why we need a counting algorithm for the approach. Let's try to find the best spot for this small explanation so that we do not have repetition in the text.}

\begin{figure}[t]
	\centering
	\includegraphics[width=1\columnwidth]{images/Comparison}
	\centering{\caption{\label{Comparison}The parameter ($Range<V_x(t)>$) varying the oscillating input flow strength at the inlet $A$ at a frequency $f_i= 0.1 Hz$: comparison between viable yeast cells, yeast cells exposed to cell death stimuli and silica beads in the glycerol-water (GW) solution.\DS{How do you do these curves? Why do they show this curvilinear behavior and not a rectilinear one? LINEA DI TENDENZA POLINOMIALE GRADO 4}}}
\end{figure}

~\fig\ref{Comparison} shows the value of the velocity range ($Range<V_x(t)>$ \DS{OK ---- no need to repeat this symbol. Once defined, you can just refer to the symbol}) for each experimental condition. The three curves are related to viable yeast cells, yeast cells exposed to cell death stimuli and silica beads in the glycerol-water solution. Each point of the curves is correlated to the amplitude of the external oscillating input flow strength $A$ with a constant frequency $f_i= 0.1 Hz$. 
Because of the fact that micro-particles of different natures are being compared, a normalization of the $Range<V_x(t)>$ to the average number of particles was carried out. This procedure was applied due to the fact that the micro-particles density is different in each experimental condition and thanks to this normalization it is possible to compare the results obtained. 
\\The micro-particles hydrodynamic response comparison in time domain was evaluated by computing the range of the velocity signal $<V_x(t)>$, as shown in \DS{\eqn(}\ref{eqn:range}) and normalizing it with respect to the average number of micro-particles $<N_p(t)>$, computed in the investigated area following the procedure described in \sect\ref{sec:method}.
From ~\fig\ref{Comparison} it is possible to notice that, for all the experimental conditions, the curve relating to yeast cells exposed to cell death stimuli is always in the middle, between the one relating to viable yeast cells and the one relating to silica beads in the glycerol-water solution.
Yeast cells vary their behavior according to their different living conditions taking on characteristics more typical of synthetic particles, i.e. silica beads, when they are exposed to death stimuli. In fact, the results show that their behavior is comparable with particles of lower density and with the fluid on which they are suspended as they exhibit no resistance to the input flows while attaining higher velocities than the yeast live cells.

\subsection{Online vs Offline}\label{sec:OnlineOffline}
\DS{Before going into the details with this part and its revision, please, consider to make all the necessary steps to identify that the camera settings are not modified by Matlab. }
To test the consistency of the two DPIV-based implementations, a subset of the experiments was tested and analyzed also through the DPIV-based online implementation, detailed in ~\tab\ref{onlineexp}. Two categories of micro-particles were considered, more precisely viable yeast cells and silica beads in the glycerol-water solution. The sample of fluid was fed into the micro-channel using an oscillating flow at a fixed frequency of $f_i= 0.1 Hz$ and five different amplitude values $A \in \{ 0.05, 0.07, 0.1, 0.15, 0.2 ml/min \}$. Process frames were acquired for a time interval of 15 $s$ for each experimental condition. 
The results obtained through the online implementation were compared with those obtained through the offline platform for the same micro-particle category and experimental conditions. \DS{measurement units}
